Compiling refinement types to dependent types

### 2020-07-22 tex/paper.tex
Add a syntax for remarks

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\crefname{lemma}{Lemma}{Lemmas}

@@

The surface language might also have other base types (for example, $\Int$),
elements of syntax (like numbers and operations on them)
as well as typing rules relating those,
but we omit them for the sake of brevity.

>>>>

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{remark}{Remark}
\crefname{lemma}{Lemma}{Lemmas}
\crefname{remark}{Remark}{Remarks}

@@

\begin{remark}\label{remark:surface_base_types}
  The surface language might also have other base types (for example, $\Int$),
  elements of syntax (like numbers and operations on them)
  as well as typing rules relating those,
  but we omit them for the sake of brevity.
\end{remark}
